\tcode{Generalisation of nth_element to a range of nths}

### 2021-12-20 draft_lundberg_nth_elements.tex
Adding missing argument S last to  one of the overloads

\begin{tabular}{ll}
Document \#:& D2375R1\\
Date: &2021-12-16 \\
Project: & Programming Language C++ \\
Audience: & LEWG \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

Draft 2021-12-16: Added clarifications and more background, explanations, wording clarifications, references, summarized performance study, applications, more questions/answers. --Based on feedback and material sent to SG9 list 2021-12-09.

@@

namespace ranges {
  template<random_access_iterator I, sentinel_for<I> S, 
  random_access_range R2, class Comp = ranges::less, class Proj = identity>
  requires sortable<I, Comp, Proj>
  constexpr I nth_element(I first, R2&& nths, Comp comp = {}, Proj proj = {});

>>>>

\begin{tabular}{ll}
Document \#:& D2375R1\\
Date: &2021-12-19 \\
Project: & Programming Language C++ \\
Audience: & LEWG \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

Draft 2021-12-16: Added clarifications and more background, explanations, wording clarifications, references, summarized performance study, applications, more questions/answers. --Based on feedback and material sent to SG9 list 2021-12-09. Synopsis: \tcode{S last} argument was missing 2021-12-19.

@@

namespace ranges {
  template<random_access_iterator I, sentinel_for<I> S, 
  random_access_range R2, class Comp = ranges::less, class Proj = identity>
  requires sortable<I, Comp, Proj>
  constexpr I nth_element(I first, R2&& nths, S last, Comp comp = {}, Proj proj = {});
